---
title: "p8105_hw1_zj2379"
author: "Zheshu Jiang"
date: "2023-09-20"
output: html_document
---
## Probelem 1
load the moderndive library and tidyverse library and then load the early_january_weather dataset
```{r}
library(moderndive)
library(tidyverse)
data("early_january_weather")
```

There are 15 following variables in the early_january_weather dataset: origin, year, month, day, hour, temp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour. Specifically, for data type, 1 varible is chr, 4 variables are int, 9 variables are dbl, and 1 variable is POSIXct. 

The dataset has 358 rows and 15 columns.  

The mean temperature is 39.58212.
```{r}
early_january_weather
mean(early_january_weather$temp)
```
create a scatterplot and save it as a pdf. 

The scatterplot exhibits an overall trend of increasing values of y  as x increases, but it shows a zigzag or sawtooth-like pattern, with intermittent fluctuations in the upward direction
```{r}
ggplot(early_january_weather, aes(x=time_hour, y=temp,color = humid))+geom_point()
ggsave("scatter_plot.pdf")
```
## Problem 2
create a data frame with a numeric vector, logical vector,  character vector, and factor vector 
```{r}
data_frame = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 10,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(c("high", "high", "high", "low", "low", "low", "medium", "medium", "medium", "medium"))
)
```

Try to take the mean of each variable in the dataframe, only the means of numeric and logical vectors can be calculated, the means of character and factor vectors cannot be calculated. 
```{r}
mean(data_frame$vec_numeric)
mean(data_frame$vec_logical)
mean(data_frame$vec_char)
mean(data_frame$vec_factor)
```
After converting variables from one type to another using as.numeric, the means of logical and factor variables become available, while the mean of factor variable remains unavailable. Since the characters are not valid numbers,as.numeric function fails to convert the characters to numeric values.
```{r, results='hide'}
as.numeric(data_frame$vec_logical)
as.numeric(data_frame$vec_char)
as.numeric(data_frame$vec_factor)
```






