---
title: "p8105_hw1_zj2379"
author: "Zheshu Jiang"
date: "2023-09-20"
output: html_document
---
## Probelem 1
```{r}
#load the moderndive library and tidyverse library and then load the early_january_weather dataset
library(moderndive)
library(tidyverse)
data("early_january_weather")
```

There are 15 following variables in the early_january_weather dataset: origin, year, month, day, hour, temp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour. Specifically, for data type, 1 variable is chr, 4 variables are int, 9 variables are dbl, and 1 variable is POSIXct. 

The dataset has 358 rows and 15 columns.  

The mean temperature is 39.58212.
```{r}
#take a look of the dataset and calculate the mean of temperature
early_january_weather
mean(early_january_weather$temp)
```

The scatterplot exhibits an overall trend of increasing values of y  as x increases, but it shows a zigzag or sawtooth-like pattern, with intermittent fluctuations in the upward direction
```{r}
#create a scatterplot and save it as a pdf. 
ggplot(early_january_weather, aes(x=time_hour, y=temp,color = humid))+geom_point()
ggsave("scatter_plot.pdf")
```
## Problem 2
```{r}
#create a data frame with a numeric vector, logical vector,  character vector, and factor vector
data_frame = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 10,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(c("high", "high", "high", "low", "low", "low", "medium", "medium", "medium", "medium"))
)
```

Only the means of numeric and logical vectors can be calculated, the means of character and factor vectors cannot be calculated. 
```{r}
# Try to take the mean of each variable in the dataframe
mean(data_frame$vec_numeric)
mean(data_frame$vec_logical)
mean(data_frame$vec_char)
mean(data_frame$vec_factor)
```
After converting variables from one type to another using as.numeric, the means of logical and factor variables become available, while the mean of factor variable remains unavailable. Since the characters are not valid numbers,as.numeric function fails to convert the characters to numeric values.
```{r, results='hide'}
# convert variables from one type to numeric using as.numeric
as.numeric(data_frame$vec_logical)
as.numeric(data_frame$vec_char)
as.numeric(data_frame$vec_factor)
```






