---
title: "p8105_hw1_zj2379"
author: "Zheshu Jiang"
date: "2023-09-20"
output: html_document
---
## Probelem 1
load the moderndive library and tidyverse library and then load the early_january_weather dataset
```{r}
library(moderndive)
library(tidyverse)
data("early_january_weather")
```
There are 15 following variables in the early_january_weather dataset: origin, year, month, day, hour, temp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour. Specifically, for data type, 1 varible is chr, 4 variables are int, 9 variables are dbl, and 1 variable is POSIXct. 

The dataset has 358 rows and 15 columns.  

The mean temperature is 39.58212.
```{r}
early_january_weather
mean(early_january_weather$temp)
```
create a scatterplot and save it as a pdf. 

The scatterplot exhibits an overall trend of increasing values of y  as x increases, but it shows a zigzag or sawtooth-like pattern, with intermittent fluctuations in the upward direction
```{r}
ggplot(early_january_weather, aes(x=time_hour, y=temp,color = humid))+geom_point()
ggsave("scatter_plot.pdf")
```



